Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-25 paper/paper.tex
conclusions

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya\ line emission that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities, either
a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$. 
The velocity dispersion in the multiphase model is consistent with a dynamical
mass of $2\times 10^{9}$ M$_{\odot}$, ten times its baryonic mass,
which can be explained if \tol\ is hosted by a dark matter halo of at least
$10^{11}$ M$_{\odot}$; cconditions similar to those of Dwarf Elliptical Galaxies.
This work shows the importance of considering multiphase
and rotation kinematics among the possible conditions shaping the
\lya\ spectra.
If future kinematic maps of \tol\ confirm the velocities found by the
multiphase model, it will be the basis to study new processes that
might be at play during priomordial galaxy evolution.
\end{abstract}

@@

Another observational test to confirm the picture provided by the
multiphase model includes the measurement of the \lya\ ionizing
continuum escape fraction. 
This model model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle (i.e. some sightlines can have
an escape fraction close to $100\%$) \citep{Gronke2016} .

@@

We acknowledge that a final confirmation of our kinematic findings has
to be provided by new observational tests of the kind we suggest.
If that were the case, this would open up a new line of more detailed
enquiries to understand how a compact dwarf galaxy can have the
structural characteristics similar to a dwarf elliptical while being
at the same time isolated and sustaining large starburst.

\section*{Acknowledgments}
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya\ data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.

>>>>

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya\ line emission that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities, either
a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$. 
The velocity dispersion in the multiphase model is consistent with a dynamical
mass of $2\times 10^{9}$ M$_{\odot}$, ten times its baryonic mass,
which can be explained if \tol\ is hosted by a dark matter halo of at least
$10^{11}$ M$_{\odot}$; cconditions similar to those of Dwarf Elliptical Galaxies.
This work shows the importance of considering multiphase
and rotation kinematics among the possible conditions shaping the
\lya\ spectra.
If future kinematic maps of \tol\ confirm the velocities found by the
multiphase model, it will be the basis to study new processes that
might be at play during primordial galaxy evolution.
\end{abstract}

@@

Another observational test to confirm the picture provided by the
multiphase model includes the measurement of the \lya\ ionizing
continuum escape fraction. 
This model model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle, i.e. some sightlines can have
an escape fraction close to $100\%$, \citep{Gronke2016}.

@@

We acknowledge that a final confirmation of our kinematic findings has
to be provided by new observational tests of the kind we suggest.
If that were the case, this would open up a new line of more detailed
enquiries to understand how a compact dwarf galaxy can have the
structural characteristics similar to a dwarf elliptical while being
at the same time isolated and sustaining large starburst.
If an evolutionary link is stablished between a phase where a \tol and dE this would b

\section*{Acknowledgments}
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya\ data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
J. E. F-R. ackwnoledges the support of J. L. Guerra in the last
writing stages of this paper.
